%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Aman Garg} \\ \vspace{3pt}
    \small +91 740-415-2804 $|$ \href{mailto:amangarg25aug@gmail.com}{\underline{amangarg25aug@gmail.com}} $|$ 
    \href{https://linkedin.com/in/ag25aug}{\underline{linkedin.com/in/ag25aug}} 
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Birla Institute of Technology and Science Pilani}{Pilani, Rajasthan}
      {Bachelor of Engineering in Computer Science \& M.Sc. in Mathematics}{Aug 2016 -- Jul 2021}
    \resumeSubheading
      {DAV Centenary Public School}{Rohtak, Haryana}
      {Class 1st to 12th}{2004 -- 2016} 
  \resumeSubHeadingListEnd


% \section{Technical Skills}
%  \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{{Java, Spring Boot, CI/CD, SQL, NoSQL, Apache Kafka}}}
%  \end{itemize}

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Walmart Global Tech India}{ }
      {Software Engineer 2}{Jul 2021 -- Present}
      \resumeItemListStart

        \resumeItem{Designed, developed, tested, and deployed software solutions at \textbf{scale} for Walmart Fulfillment Services, enabling sellers to use Walmart's \textbf{Supply Chain as a Service} and sell their products online. This is expected to \textbf{increase GMV by \$5 billion USD} by 2025 in Canada and Mexico. \textbf{Technologies used}: Java, Spring Boot, Apache Kafka, Apache Airflow, Apache Spark, Azure SQL, Azure Cosmos, Apache Hive, CI/CD, GCP}
        
        \resumeItem{Reccognised for \textbf{saving the cost of packaging 2.6 million} units per year per FC. Improved cartonization logic used in Walmart International by minimizing the number of boxes needed to pack the items. Ensured \textbf{end-to-end delivery}. Created extensive \textbf{documentation that is now used as a benchmark} for the entire team.}
        
        \resumeItem{\textbf{Team award} for developing distribution team's first \textbf{cloud-based SaaS} component FIXit to track and act on inbound exceptions in warehouse. \textbf{Reduced manpower by 75\%}. Actively collaborated with multiple teams to document and set up the initial infrastructure. New technologies learned: \textbf{GraphQL}.}
        
        \resumeItem{\textbf{Bravo award for taking the initiative to implement CI/CD} for 5 repos, driving engineering excellence.}
        
        \resumeItem{Onboarded and \textbf{mentored} 2 interns, 2 FTEs, and 4 vendors on various projects and teams.}
        
        \resumeItem{Worked in data platform team as a summer intern in 2020. Contributed in \textbf{processing around 10 million transactions per day} from all Walmart stores across the world. Internship converted to full-time position.}
        
        \resumeItem{Other achievements include receiving \textbf{1 Bravo award, 2 Team awards, and 5 Badges}; \textbf{helping HR team} create tests for campus recruitments, organizing fun events, publishing newsletters, and participating in \textbf{hackathons} to drive innovation and collaboration.}
      
      \resumeItemListEnd

    \resumeSubheading
      {Vymo}{}
      {Software Engineer Intern}{Aug 2020 -- Dec 2020}
      \resumeItemListStart
        \resumeItem{Added \textbf{8 new features} in Self-Serve platform. It helped in reducing the turnaround time of developers from \textbf{2 weeks to a few minutes}. Technologies used: Java \& Node.js}
        \resumeItem{Collaborated with multiple teams for \textbf{end-to-end} delivery of the features i.e. from designing, modeling, and development to QA sign-off, production release, documentation, and migration of old data. \textbf{Received a full-time offer} after internship.}
    \resumeItemListEnd


  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------






%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
          {\textbf{Voice assistant} $|$ \emph{Django, Python, Open AI, Generative AI, Machine Learning}}{\small{\href{https://github.com/rubal2508/Ctrl-Alt-Elite}{\underline{GitHub link}}}}
          \resumeItemListStart
            \resumeItem{Led a team of 4 to create an \textbf{AI-powered voice assistant} for an e-commerce company using ChatGPT APIs at a \textbf{hackathon}.}
            \resumeItem{Enabled user to use voice commands to perform actions like \textbf{search for ingredients}, get user sentiments, return/replace orders, and FAQs.}
            
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Instagram Bot} $|$ \emph{Python, Selenium, Web scraping, Automation}}{\small{\href{https://github.com/rubal2508/Project-InstaBot}{\underline{GitHub link}}}}
          \resumeItemListStart
            \resumeItem{\textbf{Automated Instagram processes} including login, follow/unfollow, searching, liking/viewing posts and stories.}
            \resumeItem{Created a database of popular food bloggers, tracking their posts, likes-to-followers ratio, and latest hashtags being used in the industry.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd


\section{Skills \& Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Technical Skills}{: Java, Spring Boot, Maven, CI/CD, SQL, NoSQL, Apache Kafka} \\
     \textbf{Hobbies}{: Art \& Craft, Sketching, Playing flute, Learning about history} \\
     \textbf{Leadership}{: Led and taught a team of 8 students to paint 18x6ft panels for the university's cultural fest in 3rd year.} 
    }}
 \end{itemize}



%-------------------------------------------
\end{document}
